---
title: "Feasibility Summary"
output:
  html_document:
    df_print: paged
    toc: yes
    toc_collapsed: yes
    toc_float: yes
---

## Notices

### Feasibility Query

The data presented here are the results of a feasbility evaluation performed by
the PEDSnet data and analytic coordinating center.  Because feasibility queries
require efficient completion, they entail less consultation regarding study
design, resource allocation, and data quality analysis than full study
execution, feasibility results may incompletely predict observations made
during the study.

### Confidentiality

Please treat the contents of this report as confidential, and do not
redistrubute beyond PEDSnet staff and the requester.

## Specification

### Request Description

Brief narrative summary of the request.

### Cohort Definition

* List the logical steps of the query

```{r setup, include=FALSE}
# Default taken from R notebook behavior: when knitting, wd will always be location of notebook
base_dir <- '..'
Sys.setenv(PEDSNET_SKIP_REQUEST_EXECUTION=1)
try(source('../site/run.R')) # May not be able to make db connection

# Set to "local" to read data from ../results, or another value to read from db
data_source <- if_else(config('execution_mode') == 'distribution', 'local', 'not_local')

require(tidyr)
require(knitr)
require(kableExtra)
require(stringr)
require(tibble)
require(ggplot2)

get_results <- function(tbl_name) {
  if (data_source == 'local') {
    rslt <- read_csv(paste0('../results/', tbl_name, '.csv'))
  }
  else {
    rslt <- results_tbl(tbl_name) %>% collect()
  }
rslt
}

prettify_kable <- function(data) {
  data %>% kable(digits = 4, format.args = list(big.mark = ',')) %>% 
    kable_styling(bootstrap_options = c("striped", "hover")) %>% 
    column_spec(1, bold = T, border_right = T)
}

cohort <- get_results('my_cohort_table')
```

## Results

The cohort comprises `r summarise(cohort, ct = n_distinct(person_id)) %>% pull(ct)`
patients from `r summarise(cohort, ct = n_distinct(site)) %>% pull(ct)` sites.

### Attrition

```{r attrition, echo=FALSE}
# DBI doesn't have a good way to interrogate tables in a specified schema,
# so you have to list the step logs you want to summarise (e.g. DCC + remote
# sites).
list(config('site')) %>%
  map(.f = function(x) {
    get_results(paste0(x, '_steps'))
  }) %>% 
  reduce(.f = dplyr::union) %>% 
  arrange(stamp) %>% filter(cohort != 'Start') %>% 
  select(cohort, persons) %>% prettify_kable()
```

### _Add report summary content here as subsections_

## End
