---
title: "PEDSnet Geocoding Data Quality Summary"
author: "PEDSnet Data Coordinating Center"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    df_print: paged
    toc: yes
    toc_collapsed: yes
    toc_float: yes
---

```{r setup, include=FALSE}
require(argos)
require(srcr)
require(dplyr)
require(tidyr)
require(knitr)
require(kableExtra)
require(stringr)
require(tibble)
require(ggplot2)

geocoding_report <- argos$new()

set_argos_default(geocoding_report)

config('db_src', srcr(Sys.getenv('PEDSNET_DB_SRC_CONFIG_BASE')))
config('results_name_tag', '')
config('retain_intermediates', FALSE)

get_results <- function(tbl_name) {
    rslt <- results_tbl(tbl_name) %>% collect()
}

prettify_kable <- function(data) {
  data %>% kable(digits = 4, format.args = list(big.mark = ',')) %>% 
    kable_styling(bootstrap_options = c("striped", "hover")) %>% 
    column_spec(1, bold = T, border_right = T)
}

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

```

# Broad Completeness Assessment

Using a population of patients with a valid sex, valid DOB, and at least one face-to-face encounter, we assessed the proportion of patients for whom at least one location_id is able to be linked to a geocode at the census tract and/or block group level for the 2010 and 2020 census years.

```{r}

config('results_schema', 'dqa_rox')

get_results('ecp_output_pp') %>%
  filter(check_name %in% c('ecp_tract_2020', 'ecp_block_group_2020',
                           'ecp_tract_2010', 'ecp_block_group_2010')) %>%
  mutate(check_name = case_when(check_name == 'ecp_tract_2010' ~ '2010 Census Tract',
                                check_name == 'ecp_tract_2020' ~ '2020 Census Tract',
                                check_name == 'ecp_block_group_2010' ~ '2010 Census Block Group',
                                check_name == 'ecp_block_group_2020' ~ '2020 Census Block Group')) %>%
  ggplot(aes(x = site, y = prop_with_concept, fill = site)) +
  geom_col() +
  facet_wrap(~check_name) +
  theme_minimal() +
  scale_fill_brewer(palette = 'Paired') +
  theme(legend.position = 'none',
        axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
  labs(y = 'Prop. Patients with Geocoded Location',
       x = 'Site')

```

# Pre-Normalization Residential History

## 1+ Geocoded Location History Records

Assessed the proportion of rows in the `location_history` table and patients that had at least one location history record that are able to be linked to a geocode at the census tract and/or block group level for the 2010 and 2020 census years.

```{r}
config('results_schema', 'dq_residential_history')

row_level <- get_results('pct_loc_his_records_with_fips') %>%
  pivot_longer(cols = !site) %>%
  mutate(geocode_type = case_when(grepl('2010_tract', name) ~ '2010 Census Tract',
                                  grepl('2020_tract', name) ~ '2020 Census Tract',
                                  grepl('2010_block', name) ~ '2010 Census Block Group',
                                  grepl('2020_block', name) ~ '2020 Census Block Group'),
         analysis_level = 'Row')

pt_level <- get_results('pct_pats_with_loc_his_and_fips') %>%
  pivot_longer(cols = !site) %>%
  mutate(geocode_type = case_when(grepl('2010_tract', name) ~ '2010 Census Tract',
                                  grepl('2020_tract', name) ~ '2020 Census Tract',
                                  grepl('2010_block', name) ~ '2010 Census Block Group',
                                  grepl('2020_block', name) ~ '2020 Census Block Group'),
         analysis_level = 'Patient',
         value = ifelse(is.na(value), 0, value))

row_level %>%
  dplyr::union(pt_level) %>%
  ggplot(aes(x = site, y = value, fill = analysis_level)) +
  geom_col(position = 'dodge') +
  facet_wrap(~geocode_type) +
  theme_minimal() +
  scale_fill_brewer(palette = 'Set2') +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
  labs(x = 'Site',
       y = 'Proportion with 1+ Geocode',
       fill = 'Analysis Level')

```

## Patients with 2+ Geocoded Location History Records

Using a population of patients with a valid sex, valid DOB, and at least one face-to-face encounter, we assessed the proportion of patients for whom 2 or more distinct records in the location_history table are able to be linked to a geocode at the census tract and/or block group level for the 2010 and 2020 census years.

```{r}

config('results_schema', 'dqa_rox')

get_results('ecp_output_pp') %>%
  filter(check_name %in% c('ecp_twoplus_lohis_tract_2020', 'ecp_twoplus_lohis_cbg_2020',
                           'ecp_twoplus_lohis_tract_2010', 'ecp_twoplus_lohis_cbg_2010')) %>%
  mutate(check_name = case_when(check_name == 'ecp_twoplus_lohis_tract_2010' ~ '2010 Census Tract',
                                check_name == 'ecp_twoplus_lohis_tract_2020' ~ '2020 Census Tract',
                                check_name == 'ecp_twoplus_lohis_cbg_2010' ~ '2010 Census Block Group',
                                check_name == 'ecp_twoplus_lohis_cbg_2020' ~ '2020 Census Block Group')) %>%
  ggplot(aes(x = site, y = prop_with_concept, fill = site)) +
  geom_col() +
  facet_wrap(~check_name) +
  theme_minimal() +
  theme(legend.position = 'none',
        axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
  scale_fill_brewer(palette = 'Paired') +
  labs(y = 'Prop. Patients with 2+ Geocoded Locations',
       x = 'Site')

```

## Patients without Location History Records

Assessed the proportion of patients who did not have evidence of any record in the `location_history` table.

```{r}

config('results_schema', 'dq_residential_history')

get_results('pct_pats_without_loc_his_record') %>%
  ggplot(aes(x = site, y = pct_pats_missing_loc_his_record, fill = site)) +
  geom_col() +
  theme_minimal() +
  theme(legend.position = 'none',
        axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
  scale_fill_brewer(palette = 'Paired') +
  labs(x = 'Site',
       y = 'Prop. Patients Missing Loc. His. Record')

```

## Duplicate Location History Records

Identified duplicate records by checking for repeated combinations of `person_id`, `census_block_group`, `start_date`, and `end_date` in the `location_history` table, then calculates the total count of duplicates and distinct duplicates for census year, and finally computes the percentage of duplicates for those census years.

```{r}

row_level <- get_results('pct_loc_his_records_dups') %>%
  select(site, pct_loc_his_dup_records_2010, pct_loc_his_dup_records_2020) %>%
  pivot_longer(!site) %>%
  mutate(geocode_year = ifelse(grepl('2010', name), '2010 Census Block Group', 
                               '2020 Census Block Group'),
         analysis_level = 'Row',
         value = ifelse(is.na(value), 0, value))

pt_level <- get_results('pct_pats_with_dups') %>%
  select(site, pct_pats_dup_records_2010, pct_pats_dup_records_2020) %>%
  pivot_longer(!site) %>%
  mutate(geocode_year = ifelse(grepl('2010', name), '2010 Census Block Group', 
                               '2020 Census Block Group'),
         analysis_level = 'Patient',
         value = ifelse(is.na(value), 0, value))

row_level %>%
  union(pt_level) %>%
  ggplot(aes(x = site, y = value, fill = analysis_level)) +
  geom_col(position = 'dodge') +
  facet_wrap(~geocode_year) +
  theme_minimal() +
  scale_fill_brewer(palette = 'Set2') +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
  labs(x = 'Site',
       y = 'Proportion Duplicates',
       fill = 'Analysis Level')

```

## Overlapping Geocode Dates

Identifies overlapping date ranges for the same `person_id` and `census_block_group` within each census year, and found the proportion of both rows and patients that had overlapping records.

```{r}

row_level <- get_results('pct_loc_his_records_with_overlapping_geocode_dates') %>%
  select(site, pct_loc_his_recs_with_overlap_2010_cbg_dates, 
         pct_loc_his_recs_with_overlap_2020_cbg_dates) %>%
  pivot_longer(!site) %>%
  mutate(geocode_year = ifelse(grepl('2010', name), '2010 Census Block Group', 
                               '2020 Census Block Group'),
         analysis_level = 'Row',
         value = ifelse(is.na(value), 0, value))

pt_level <- get_results('pct_pats_with_overlapping_geocode_dates') %>%
  select(site, pct_pats_with_overlap_2010_cbg_dates, 
         pct_pats_with_overlap_2020_cbg_dates) %>%
  pivot_longer(!site) %>%
  mutate(geocode_year = ifelse(grepl('2010', name), '2010 Census Block Group', 
                               '2020 Census Block Group'),
         analysis_level = 'Patient',
         value = ifelse(is.na(value), 0, value))

row_level %>%
  union(pt_level) %>%
  ggplot(aes(x = site, y = value, fill = analysis_level)) +
  geom_col(position = 'dodge') +
  facet_wrap(~geocode_year) +
  theme_minimal() +
  scale_fill_brewer(palette = 'Set2') +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
  labs(x = 'Site',
       y = 'Proportion with Overlapping Dates',
       fill = 'Analysis Level')

```

## Patients with 30 Day Gap b/w Records

Checks whether a patient's previous location history record ends more than 30 days before their next record starts

```{r}

get_results('pct_pats_with_30d_gap') %>%
  ggplot(aes(x = site, y = pct_pats_with_30_day_gap, fill = site)) +
  geom_col() +
  theme_minimal() +
  theme(legend.position = 'none',
        axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
  scale_fill_brewer(palette = 'Paired') +
  labs(x = 'Site',
       y = 'Prop. Patients with 30 Day Gap')

```

## Patients with Encompassing Location History

Calculates the percentage of patients who have at least one location history record for each year from 2009 to 2024

```{r}

get_results('pct_pats_per_year_with_encompassing_loc_his') %>%
  ggplot(aes(x = year, y = pct_pats_with_loc_his_for_year, color = site)) +
  geom_line() +
  theme_minimal() +
  scale_color_brewer(palette = 'Paired') +
  labs(x = 'Year',
       y = 'Prop. Patients with Full History', 
       color = 'Site')

```
