---
title: "Study Summary"
output:
  pdf_document: default
  html_notebook: default
---

# PEDSnet Data Request

```{r include=FALSE}
require(tibble)
require(knitr)
source('../code/driver.R')
source('../code/config.R')
source('../code/req_info.R')
source('../code/setup.R')
source('../code/util_tbl.R')
source('../code/setup.R')
source('../site/site_info.R')
source('./summary_functions.R')

.env_setup()
```

## Request Information

Please enter the name of the demographics table for your study for the variable "table_name" below. 

Alter the field "Date Range" below to indicate the earliest and latest dates included in your study.

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
kable(tribble( ~Item, ~Value,
               'Title', config('title'),
               'Requester', config('requester_name'),
               'Sponsoring Member', config('requester_site'),
               'CDM Version', config('cdm_version'),
               'Package Version', config('req_version'),
               'Date Range', "2009-2018"))

table_name <- "cohort_demographics"
```

### Study Description

Provide a summary of the scientific specification here.

### Inclusion Criteria

The criteria for inclusion of data in the request are described here.

If you have an attrition table (in .csv format), please include it below.


```{r, echo = F}

attrition <- read.csv('../results/fake_attrition.csv', header = T)
attrition <- as.data.frame(attrition)
knitr::kable(attrition, caption = "Attrition Table")
  
```

#### Cohort Definition

If the request involves creation of one or more cohorts, you may wish
to summarize their characteristics here

### Output

Please describe the deliverable for this study.

End of User Input.

## Cohort Demographics Summary

```{r, echo=  F}
table_one <- connect_table(table_name)

gender_summary <- gender_breakdown(table_one) %>% as.data.frame() %>% make_percentage('Patient_Count')
race_summary <- race_breakdown(table_one) %>% as.data.frame() %>% make_percentage('Patient_Count')
ethnicity_summary <- ethnicity_breakdown(table_one) %>% as.data.frame() %>% make_percentage('Patient_Count')
site_summary <- site_breakdown(table_one) %>% as.data.frame() %>% make_percentage('Patient_Count')

total_patients <- get_patient_count(table_one) %>% as.data.frame()
Population <- c("Total Count", paste("Gender: ", gender_summary$gender_concept_name),
                paste("Race: ", race_summary$race_concept_name),
                paste("Ethnicity: ", ethnicity_summary$ethnicity_concept_name),
                paste("Site: ", site_summary$site))
Patient_Count <- c(total_patients[[1]], gender_summary$Patient_Count, race_summary$Patient_Count,
            ethnicity_summary$Patient_Count, site_summary$Patient_Count)
Patient_Count[Patient_Count < 11] <- NA

Percentage <- c(100, gender_summary$Percent_Total, race_summary$Percent_Total,
                ethnicity_summary$Percent_Total, site_summary$Percent_Total)

summary_table <- data.frame(Population, Patient_Count, Percentage)
knitr::kable(summary_table, caption = "Demographic Summary")
```

```{r, echo = F}
barplot(height = as.integer(gender_summary$Percent_Total), names.arg = gender_summary$gender_concept_name, col = 'blue', ylab = 'Percentage', main = "Breakdown of Cohort by Gender", las = 2)
```

```{r, echo = F}
barplot(height = as.integer(race_summary$Percent_Total), names.arg = race_summary$race_concept_name, col = 'blue', ylab = 'Percentage', main = "Breakdown of Cohort by Race", las = 2)
```

```{r, echo = F}
barplot(height = as.integer(ethnicity_summary$Percent_Total), names.arg = ethnicity_summary$ethnicity_concept_name, col = 'blue', ylab = 'Percentage', main = "Breakdown of Cohort by Ethnicity", las = 2)

```

```{r, echo = F}
barplot(height = as.integer(site_summary$Percent_Total), names.arg = site_summary$site, col = 'blue', ylab = 'Percentage', main = "Breakdown of Cohort by Site", las = 2)
```

```{r, echo = F}
bdays <- table_one %>%
  mutate(Birth_Year = as.integer(year(birth_datetime))) %>%
  filter(Birth_Year >= 2009) %>%
  group_by(Birth_Year) %>%
  summarize(Counts = n()) %>%
  as.data.frame() %>%
  arrange(Birth_Year) %>%
  make_percentage(field = "Counts")

barplot(height = as.integer(bdays$Percent_Total), names.arg = bdays$Birth_Year, col = 'blue', ylab = 'Percentage', main = "Distribution of Cohort Birth Years", las = 2)
```

